Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019

### 2023-03-13 products/paper/main.qmd
Add paragraph to address redshirt issue #34 and footnoote to address issue #34 and #35

>>>>

Using grade-age comparisons to infer grade retention may inadvertently capture cases of "academic redshirting" in which parents intentionally delay their child's kindergarten enrollment by a year. @frederick_have_2008 suggest that academic redshirting is in many cases be a form of preemptive retention for children with developmental delays and thus the error induced by these false positive cases may be minimal. However, @bassok_academic_2013 have shown that academic redshirting is more common among white and SES privileged parents, suggesting that the demographic covariates of academic redshirting may operate in the opposite direction of grade retention. Regardless, academic redshirting should be of minimal concern for the measure of CBEG used here. Academic redshirting most frequently occurs for students whose birthdays fall close to the cutoff period for enrollment [@graue_redshirting_2000; @bassok_academic_2013]. Therefore, academic redshirts spend most of a given school year at the older, but correct, modal age for their grade and most of these students will not be identified as CBEG.[^redshirts]

[^redshirts]: Analysis of the probability of being CBEG by race and grade, shown in the supplementary materials, indicates that Black and Latino children in kindergarten are less likely to be CBEG than White children, which may be a consequence of redshirting. However, these differences quickly reverse direction by first grade. As a sensitivity analysis, I repeated the main analysis shown here separately for students in elementary (1st-5th), middle school (6th-8th), and high school (9th-12th) grades. These results are presented in the supplementary materials. Although more statistically noisy due to smaller sample sizes, those results are consistent with the conclusions drawn here.
